How Optimal is Word-Referent Identification Under Multimodal Uncertainty?

### 2019-03-15 Writeup/ms.Rmd
revisions

```{r load_packages, include = FALSE}
library(papaja)
library(readr)
library(tidyr)
library(ggplot2)
library(cowplot)
library(knitr)
library(boot)
library(dplyr)
library(langcog)
library(ggthemes)
library(broom)
#library("knitcitations")
#cleanbib()
#options("citation_format" = "pandoc")
```

@@

@@

@@

@@

#Data subseting

#Experiment 1
##############

sound_all_exp1 <- exp1_good %>%
    filter(condition == "sound")

concept_all_exp1 <- exp1_good %>%
    filter(condition == "concept")

joint_all_exp1 <- exp1_good %>%
    filter(condition == "joint")

#Summary

sounds_exp1 <- exp1_good %>%
  filter(condition == "sound") %>%
  group_by(sound_dist) %>%
  dplyr::summarise(mean = mean(answer),
                   sd = sd(answer),
                   n = n()) %>%
  mutate(se = sd / sqrt(n),
         lower = mean - qt(1 - (0.05 / 2), n - 1) * se,
         upper = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
  select(-sd, -n, -se,) %>%
  mutate(Experiment="Experiment 1", 
         Condition="Auditory") %>%
  rename(distance = sound_dist)

concepts_exp1 <- exp1_good %>%
  filter(condition == "concept") %>%
  group_by(concept_dist) %>%
  dplyr::summarise(mean = mean(answer),
                   sd = sd(answer),
                   n = n()) %>%
  mutate(se = sd / sqrt(n),
         lower = mean - qt(1 - (0.05 / 2), n - 1) * se,
         upper = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
  select(-sd, -n, -se,) %>%
  mutate(Experiment="Experiment 1", 
         Condition="Visual") %>%
  rename(distance = concept_dist)

joint_exp1 <- exp1_good %>%
  filter(condition == "joint") %>%
  group_by(concept_dist, sound_dist) %>%
  summarise(mean = mean(answer)) %>%
  mutate(Experiment="Experiment 1", 
         Condition="Joint")

#Experiment2
############

sound_all_exp2 <- exp2_good %>%
    filter(condition == "sound")

concept_all_exp2 <- exp2_good %>%
    filter(condition == "concept")

joint_all_exp2 <- exp2_good %>%
    filter(condition == "joint")

#Summary
sounds_exp2 <- exp2_good %>%
  filter(condition == "sound") %>%
  group_by(sound_dist) %>%
  dplyr::summarise(mean = mean(answer),
                   sd = sd(answer),
                   n = n()) %>%
  mutate(se = sd / sqrt(n),
         lower = mean - qt(1 - (0.05 / 2), n - 1) * se,
         upper = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
  select(-sd, -n, -se,) %>%
  mutate(Experiment="Experiment 2", 
         Condition="Auditory") %>%
  rename(distance = sound_dist)

concepts_exp2 <- exp2_good %>%
  filter(condition == "concept") %>%
  group_by(concept_dist) %>%
  dplyr::summarise(mean = mean(answer),
                   sd = sd(answer),
                   n = n()) %>%
  mutate(se = sd / sqrt(n),
         lower = mean - qt(1 - (0.05 / 2), n - 1) * se,
         upper = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
  select(-sd, -n, -se,) %>%
  mutate(Experiment="Experiment 2", 
         Condition="Visual") %>%
  rename(distance = concept_dist)

joint_exp2 <- exp2_good %>%
  filter(condition == "joint") %>%
  group_by(concept_dist, sound_dist) %>%
  summarise(mean = mean(answer)) %>%
  mutate(Experiment="Experiment 2", 
         Condition="Joint")

#Experiment3
############

sound_all_exp3 <- exp3_good %>%
    filter(condition == "sound")

concept_all_exp3 <- exp3_good %>%
    filter(condition == "concept")

joint_all_exp3 <- exp3_good %>%
    filter(condition == "joint")

#Summary
sounds_exp3 <- exp3_good %>%
  filter(condition == "sound") %>%
  group_by(sound_dist) %>%
  dplyr::summarise(mean = mean(answer),
                   sd = sd(answer),
                   n = n()) %>%
  mutate(se = sd / sqrt(n),
         lower = mean - qt(1 - (0.05 / 2), n - 1) * se,
         upper = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
  select(-sd, -n, -se,) %>%
  mutate(Experiment="Experiment 3", 
         Condition="Auditory") %>%
  rename(distance = sound_dist)

concepts_exp3 <- exp3_good %>%
  filter(condition == "concept") %>%
  group_by(concept_dist) %>%
  dplyr::summarise(mean = mean(answer),
                   sd = sd(answer),
                   n = n()) %>%
  mutate(se = sd / sqrt(n),
         lower = mean - qt(1 - (0.05 / 2), n - 1) * se,
         upper = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
  select(-sd, -n, -se,) %>%
  mutate(Experiment="Experiment 3", 
         Condition="Visual") %>%
  rename(distance = concept_dist)

joint_exp3 <- exp3_good %>%
  filter(condition == "joint") %>%
  group_by(concept_dist, sound_dist) %>%
  summarise(mean = mean(answer)) %>%
  mutate(Experiment="Experiment 3", 
         Condition="Joint")

#Combine all
exp_uni_data <- bind_rows(sounds_exp1, concepts_exp1,
                     sounds_exp2, concepts_exp2,
                     sounds_exp3, concepts_exp3)

@@

```{r model, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Illustration of the model using simulated data. A word category is defined as the joint bivariate distribution of an auditory category (horizontal, bottom panel) and a visual semantic category (vertical, left panel). Upon the presentation of a word token $w$, participants guess whether it is sampled from the word type $W_1$ or from the word type $W_2$. Decision threshold is where the guessing probability is 0.5."}
knitr::include_graphics("pictures/model.png", dpi = 108)
```

@@

```{r echo=FALSE}

#Bootstrap sample of parameters

lmfit <- function(data, indices) {

  myd = data[indices, ]

  s_data <- myd %>%
    filter(condition == "sound")

  v_data <- myd %>%
    filter(condition == "concept")

  j_data <- myd %>%
    filter(condition == "joint")

  s_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))), data=s_data, start = list(e=0, vrA=2), nls.control(warnOnly = TRUE))

 c_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), data=v_data, start = list(e=0, vrV=2), nls.control(warnOnly = TRUE))

 j_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), data=j_data, start = list(e=0, vrA_j=2, vrV_j=2), nls.control(warnOnly = TRUE))

  s_va <- coef(s_nl)["vrA"]
  s_e <- coef(s_nl)["e"]

  v_va <- coef(c_nl)["vrV"]
  v_e <- coef(c_nl)["e"]

  decision_ideal=v_va/s_va

  j_va_s=coef(j_nl)["vrA_j"]
  j_va_v=coef(j_nl)["vrV_j"]
  j_e=coef(j_nl)["e"]

  decision_fit=j_va_v/j_va_s

  preference = decision_fit/decision_ideal

  MyBoot=c(s_va, s_e, v_va, v_e, j_va_s, j_va_v, j_e, decision_ideal, decision_fit, preference)

  return(MyBoot)

#results1 <- boot(data=exp1_good, statistic = lmfit, R = 10000)

#dataSave1 <- data.frame(matrix(ncol = 5, nrow = 0))
#data_names <- c("variable", "estimate", "lower","upper", "Experiment")
#colnames(dataSave1) <- data_names

#Auditory variance:
#audVar=boot.ci(results1, index = 1, type = c("bca"), conf = 0.95)

#v1 <- data.frame('audVar', as.numeric(audVar$t0), as.numeric(audVar$bca[4]), as.numeric(audVar$bca[5]), 'Exp1')
#  colnames(v1) <- data_names

#Auditory bias:
#audBias=boot.ci(results1, index = 2, type = c("bca"), conf = 0.95)

#v2 <- data.frame('audBias', as.numeric(audBias$t0), as.numeric(audBias$bca[4]), as.numeric(audBias$bca[5]), 'Exp1')
#colnames(v2) <- data_names

#Visual variance:
#visVar=boot.ci(results1, index = 3, type = c("bca"), conf = 0.95)

#v3 <- data.frame('visVar', as.numeric(visVar$t0), as.numeric(visVar$bca[4]), as.numeric(visVar$bca[5]), 'Exp1')
#colnames(v3) <- data_names

#Visual bias:
#visBias=boot.ci(results1, index = 4, type = c("bca"), conf = 0.95)

#v4 <- data.frame('visBias', as.numeric(visBias$t0), as.numeric(visBias$bca[4]), as.numeric(visBias$bca[5]), 'Exp1')
#colnames(v4) <- data_names

#Bimodal Auditory variance:
#audVarBi=boot.ci(results1, index = 5, type = c("bca"), conf = 0.95)

#v5 <- data.frame('audVarBi', as.numeric(audVarBi$t0), as.numeric(audVarBi$bca[4]), as.numeric(audVarBi$bca[5]), 'Exp1')
#colnames(v5) <- data_names

#Bimodal Visual variance:
#visVarBi=boot.ci(results1, index = 6, type = c("bca"), conf = 0.95)

#v6 <- data.frame('visVarBi', as.numeric(visVarBi$t0), as.numeric(visVarBi$bca[4]), as.numeric(visVarBi$bca[5]), 'Exp1')
#colnames(v6) <- data_names

#Bimodal bias:
#BiasBi=boot.ci(results1, index = 7, type = c("bca"), conf = 0.95)

#v7 <- data.frame('BiasBi', as.numeric(BiasBi$t0), as.numeric(BiasBi$bca[4]), as.numeric(BiasBi$bca[5]), 'Exp1')
#colnames(v7) <- data_names

#Ideal modality wieghing
#prefIdeal=boot.ci(results1, index = 8, type = c("bca"), conf = 0.95)

#v8 <- data.frame('prefIdeal', as.numeric(prefIdeal$t0), as.numeric(prefIdeal$bca[4]), as.numeric(prefIdeal$bca[5]), 'Exp1')
#colnames(v8) <- data_names

#fit modality wieghing
#prefFit=boot.ci(results1, index = 9, type = c("bca"), conf = 0.95)

#v9 <- data.frame('prefFit', as.numeric(prefFit$t0), as.numeric(prefFit$bca[4]), as.numeric(prefFit$bca[5]), 'Exp1')
#colnames(v9) <- data_names

#Modality bias 
#bias=boot.ci(results1, index = 10, type = c("bca"), conf = 0.95)

#v10 <- data.frame('bias', as.numeric(bias$t0), as.numeric(bias$bca[4]), as.numeric(bias$bca[5]), 'Exp1')
#colnames(v10) <- data_names

#dataSave1 <- bind_rows(dataSave1, v1, v2, v3, v4, v5, v6, v7, v8, v9, v10)

#feather::write_feather(dataSave1, "dataExp1.feather")

dataSave1 <- feather::read_feather("dataExp1.feather")

###### Extract values from saved data 
##To reproduce the values, please uncomment the previous code following the function "lmfit"

audVar_val=dataSave1$estimate[which(dataSave1$variable == "audVar")]
audVar_ci1=dataSave1$lower[which(dataSave1$variable == "audVar")]
audVar_ci2=dataSave1$upper[which(dataSave1$variable == "audVar")]

audBias_val=-dataSave1$estimate[which(dataSave1$variable == "audBias")]
audBias_ci1=-dataSave1$upper[which(dataSave1$variable == "audBias")]
audBias_ci2=-dataSave1$lower[which(dataSave1$variable == "audBias")]

visVar_val=dataSave1$estimate[which(dataSave1$variable == "visVar")]
visVar_ci1=dataSave1$lower[which(dataSave1$variable == "visVar")]
visVar_ci2=dataSave1$upper[which(dataSave1$variable == "visVar")]

visBias_val=-dataSave1$estimate[which(dataSave1$variable == "visBias")]
visBias_ci1=-dataSave1$upper[which(dataSave1$variable == "visBias")]
visBias_ci2=-dataSave1$lower[which(dataSave1$variable == "visBias")]

audVarBi_val=dataSave1$estimate[which(dataSave1$variable == "audVarBi")]
audVarBi_ci1=dataSave1$lower[which(dataSave1$variable == "audVarBi")]
audVarBi_ci2=dataSave1$upper[which(dataSave1$variable == "audVarBi")]

visVarBi_val=dataSave1$estimate[which(dataSave1$variable == "visVarBi")]
visVarBi_ci1=dataSave1$lower[which(dataSave1$variable == "visVarBi")]
visVarBi_ci2=dataSave1$upper[which(dataSave1$variable == "visVarBi")]

BiasBi_val=-dataSave1$estimate[which(dataSave1$variable == "BiasBi")]
BiasBi_ci1=-dataSave1$upper[which(dataSave1$variable == "BiasBi")]
BiasBi_ci2=-dataSave1$lower[which(dataSave1$variable == "BiasBi")]

prefIdeal_val_1=dataSave1$estimate[which(dataSave1$variable == "prefIdeal")]
prefIdeal_ci1_1=dataSave1$lower[which(dataSave1$variable == "prefIdeal")]
prefIdeal_ci2_1=dataSave1$upper[which(dataSave1$variable == "prefIdeal")]

prefFit_val_1=dataSave1$estimate[which(dataSave1$variable == "prefFit")]
prefFit_ci1_1=dataSave1$lower[which(dataSave1$variable == "prefFit")]
prefFit_ci2_1=dataSave1$upper[which(dataSave1$variable == "prefFit")]

#Fit the posteriors to the reponses

##Experiment 1
#############

#Posterior for auditory-only condition
sound_nl1 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))), data=sound_all_exp1, start = list(e=0, vrA=2))

#Posterior for visual-only condition
concept_nl1 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), data=concept_all_exp1, start = list(e=0, vrV=2))

#Posterior for audio-visual condition (this is the descriptive model)
joint_nl1 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), data=joint_all_exp1, start = list(e=0, vrA_j=2, vrV_j=2))

##extract coefficient
eA_nl1 <- coef(sound_nl1)["e"]
vrA_nl1 <- coef(sound_nl1)["vrA"]

eV_nl1 <- coef(concept_nl1)["e"]
vrV_nl1 <- coef(concept_nl1)["vrV"]

eJ_nl1 <- coef(joint_nl1)["e"]
vrJ_A_nl1 <- coef(joint_nl1)["vrA_j"]
vrJ_V_nl1 <- coef(joint_nl1)["vrV_j"]
#######

### the fit functions
x <- seq(0, 4, 0.01)

y_sound_nl1 <- predict(sound_nl1, list(sound_dist = x), type="response")
y_concept_nl1 <- predict(concept_nl1, list(concept_dist = x), type="response")

uniS_nl1 <- data.frame(distance=x, prediction=y_sound_nl1) %>%
  mutate(Condition = 'Auditory', 
         Experiment ='Experiment 1')

uniV_nl1 <- data.frame(distance=x, prediction=y_concept_nl1) %>%
  mutate(Condition = 'Visual',
         Experiment ='Experiment 1')

##Experiment 2
###############

sound_nl2 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))), data=sound_all_exp2, start = list(e=0, vrA=2))

concept_nl2 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), data=concept_all_exp2, start = list(e=0, vrV=2))

joint_nl2 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), data=joint_all_exp2, start = list(e=0, vrA_j=2, vrV_j=2))

##extract coefficient
eA_nl2 <- coef(sound_nl2)["e"]
vrA_nl2 <- coef(sound_nl2)["vrA"]

eV_nl2 <- coef(concept_nl2)["e"]
vrV_nl2 <- coef(concept_nl2)["vrV"]

eJ_nl2 <- coef(joint_nl2)["e"]
vrJ_A_nl2 <- coef(joint_nl2)["vrA_j"]
vrJ_V_nl2 <- coef(joint_nl2)["vrV_j"]
#######

### the fit functions
x <- seq(0, 4, 0.01)

y_sound_nl2 <- predict(sound_nl2, list(sound_dist = x), type="response")
y_concept_nl2 <- predict(concept_nl2, list(concept_dist = x), type="response")

uniS_nl2 <- data.frame(distance=x, prediction=y_sound_nl2) %>%
  mutate(Condition = 'Auditory', 
         Experiment ='Experiment 2')

uniV_nl2 <- data.frame(distance=x, prediction=y_concept_nl2) %>%
  mutate(Condition = 'Visual', 
         Experiment ='Experiment 2')

##Experiment 3
###############

sound_nl3 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))), data=sound_all_exp3, start = list(e=0, vrA=2))

concept_nl3 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), data=concept_all_exp3, start = list(e=0, vrV=2))

joint_nl3 <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), data=joint_all_exp3, start = list(e=0, vrA_j=2, vrV_j=2))

##extract coefficient
eA_nl3 <- coef(sound_nl3)["e"]
vrA_nl3 <- coef(sound_nl3)["vrA"]

eV_nl3 <- coef(concept_nl3)["e"]
vrV_nl3 <- coef(concept_nl3)["vrV"]

eJ_nl3 <- coef(joint_nl3)["e"]
vrJ_A_nl3 <- coef(joint_nl3)["vrA_j"]
vrJ_V_nl3 <- coef(joint_nl3)["vrV_j"]
#######

### the fit functions
x <- seq(0, 4, 0.01)

y_sound_nl3 <- predict(sound_nl3, list(sound_dist = x), type="response")
y_concept_nl3 <- predict(concept_nl3, list(concept_dist = x), type="response")

uniS_nl3 <- data.frame(distance=x, prediction=y_sound_nl3) %>%
  mutate(Condition = 'Auditory', 
         Experiment ='Experiment 3')

uniV_nl3 <- data.frame(distance=x, prediction=y_concept_nl3) %>%
  mutate(Condition = 'Visual', 
         Experiment ='Experiment 3')

#### Combine all the fit functions
all_uni_model <- bind_rows(uniS_nl1, uniV_nl1,
                           uniS_nl2, uniV_nl2,
                           uniS_nl3, uniV_nl3)

### plot unimodal data + fit functions 
all_plot <- ggplot(exp_uni_data, 
       aes(x = distance, y = mean)) + 
  #geom_point()+
  geom_pointrange(aes(ymin = lower, ymax = upper), 
                  position = position_dodge(width = .1), size = 0.4, fatten = 2) + 
  #geom_line(data=uniV,aes(x=xV, y=yV))+
  geom_line(data=all_uni_model, aes(x=distance, y=prediction), col='black')+
  xlab("Distance") +ylab("Prob. different")+
  scale_y_continuous(limits = c(0, 1))+#theme(aspect.ratio = 0.7)+
  theme_few()+
  theme(aspect.ratio = 0.7) + facet_grid(Experiment ~ Condition)
  #stat_function(fun = Logistic_v, colour="red"))

@@

Although the paradigm is within-subjects, we did not have enough statistical power to fit a different model for each individual participant.^[We had a relatively high number of trials spanning all possible audio-visual matchings. Getting enough data points per trial per participant would have required running the online experimental for a much longer time (more than an hour). This could have increased significantly the dropout rate and possibly affected the quality of the data collected online.] Instead, models were constructed with data collapsed across all participants. That being said, we will also analyze the distribution of individual responses. The fit was done with a nonlinear least squares regression using the NLS package in R [@bates88]. We computed the values of the parameters, as well as their 95% confidence intervals, through non-parametric bootstrap (using 10000 iterations).

@@

all_plot

@@

```{r  echo=FALSE}

###Models to be tested against responses in the bimodal condition

#Descriptive model without a terms for response bias 
model_fit0 <- function (x,y) {
   1/(1 + exp((-4/vrJ_A_nl1)*x+(-4/vrJ_V_nl1)*y+(8/vrJ_A_nl1)+(8/vrJ_V_nl1)))
}

##Experiment 1
##############

#Descriptive model (parameters are derived from fit to bimodal data)
model_fit1 <- function (x,y) {
   1/(1 + (1-eJ_nl1)*exp((-4/vrJ_A_nl1)*x+(-4/vrJ_V_nl1)*y+(8/vrJ_A_nl1)+(8/vrJ_V_nl1)))
}

#The optimal model (parameters are derived from fit to unimodal data)
model_ideal1 <- function (x,y) {
    1/(1 + (1-eJ_nl1)*exp((-4/vrA_nl1)*x+(-4/vrV_nl1)*y+(8/vrA_nl1)+(8/vrV_nl1)))
}

#The sound-only model
model_sound1 <- function (x,y) {
  1/(1 + (1-eJ_nl1)*exp((-4/vrA_nl1)*x+(8/vrA_nl1)))
}

#The visual-only model
model_concept1 <- function (x,y) {
  1/(1 + (1-eJ_nl1)*exp((-4/vrV_nl1)*y+(8/vrV_nl1)))
}

##Experiment 2
##############

#Descriptive model (parameters are derived from fit to bimodal data)
model_fit2 <- function (x,y) {
   1/(1 + (1-eJ_nl2)*exp((-4/vrJ_A_nl2)*x+(-4/vrJ_V_nl2)*y+(8/vrJ_A_nl2)+(8/vrJ_V_nl2)))
}

#The optimal model (parameters are derived from fit to unimodal data)
model_ideal2 <- function (x,y) {
    1/(1 + (1-eJ_nl2)*exp((-4/vrA_nl2)*x+(-4/vrV_nl2)*y+(8/vrA_nl2)+(8/vrV_nl2)))
}

#The sound-only model
model_sound2 <- function (x,y) {
  1/(1 + (1-eJ_nl2)*exp((-4/vrA_nl2)*x+(8/vrA_nl2)))
}

#The visual-only model
model_concept2 <- function (x,y) {
  1/(1 + (1-eJ_nl2)*exp((-4/vrV_nl2)*y+(8/vrV_nl2)))
}

##Experiment 3
##############

#Descriptive model (parameters are derived from fit to bimodal data)
model_fit3 <- function (x,y) {
   1/(1 + (1-eJ_nl3)*exp((-4/vrJ_A_nl3)*x+(-4/vrJ_V_nl3)*y+(8/vrJ_A_nl3)+(8/vrJ_V_nl3)))
}

#The optimal model (parameters are derived from fit to unimodal data)
model_ideal3 <- function (x,y) {
    1/(1 + (1-eJ_nl3)*exp((-4/vrA_nl3)*x+(-4/vrV_nl3)*y+(8/vrA_nl3)+(8/vrV_nl3)))
}

#The sound-only model
model_sound3 <- function (x,y) {
  1/(1 + (1-eJ_nl3)*exp((-4/vrA_nl3)*x+(8/vrA_nl3)))
}

#The visual-only model
model_concept3 <- function (x,y) {
  1/(1 + (1-eJ_nl3)*exp((-4/vrV_nl3)*y+(8/vrV_nl3)))
}

```{r echo=FALSE, fig.width=7, fig.height=8}

#Generate prediction in the bimodal condition

models_exp1 <- joint_exp1 %>% 
  rename(joint = mean) %>%
  mutate(Descriptive = model_fit1(sound_dist, concept_dist)) %>%
  mutate(Optimal = model_ideal1(sound_dist, concept_dist)) %>%
  mutate(Auditory = model_sound1(sound_dist, concept_dist)) %>%
  mutate(Visual = model_concept1(sound_dist, concept_dist)) %>%
  gather(model, pred, Visual, Auditory, Optimal, Descriptive) %>%
  mutate(experiment = 'Experiment 1')

models_exp2 <- joint_exp2 %>% 
  rename(joint = mean) %>%
  mutate(Descriptive = model_fit2(sound_dist, concept_dist)) %>%
  mutate(Optimal = model_ideal2(sound_dist, concept_dist)) %>%
  mutate(Auditory = model_sound2(sound_dist, concept_dist)) %>%
  mutate(Visual = model_concept2(sound_dist, concept_dist)) %>%
  gather(model, pred, Visual, Auditory, Optimal, Descriptive) %>%
  mutate(experiment = 'Experiment 2')

models_exp3 <- joint_exp3 %>% 
  rename(joint = mean) %>%
  mutate(Descriptive = model_fit3(sound_dist, concept_dist)) %>%
  mutate(Optimal = model_ideal3(sound_dist, concept_dist)) %>%
  mutate(Auditory = model_sound3(sound_dist, concept_dist)) %>%
  mutate(Visual = model_concept3(sound_dist, concept_dist)) %>%
  gather(model, pred, Visual, Auditory, Optimal, Descriptive) %>%
  mutate(experiment = 'Experiment 3')

##Combine all predictions

models_all <- bind_rows (models_exp1, models_exp2, models_exp3)

models_all$model <- factor(models_all$model, levels = c('Visual','Auditory', 'Optimal', 'Descriptive'))

correlation_plot <- ggplot(models_all, 
       aes(x = pred, y = joint, col = factor(concept_dist), 
           shape = factor(sound_dist))) + 
  geom_point(size =1)+
  scale_colour_solarized()+
 #geom_pointrange(aes(ymin = summary_ci_lower, ymax = summary_ci_upper), 
  #                position = position_dodge(width = .1), size=0.2) +

  geom_abline(slope = 1, lty = 2) +
  xlab("Predictions") +ylab("Human data")+
  facet_grid(experiment ~ model)+
  theme_few()+
theme(aspect.ratio = 0.7, 
      axis.text=element_text(size=6),
      strip.text.y = element_text(size = 8))+
  guides(color=guide_legend(title="Visual Distance")) +
  guides(shape=guide_legend(title="Auditory Distance"))

#Correlation values

#Exp 1
optimal_1 <- subset(models_all, model=='Optimal' & experiment=='Experiment 1')
descriptive_1 <- subset(models_all, model=='Descriptive' & experiment=='Experiment 1')
auditory_1 <- subset(models_all, model=='Auditory' & experiment=='Experiment 1')
visual_1 <- subset(models_all, model=='Visual' & experiment=='Experiment 1')

R2_optimal_1  <- cor(optimal_1$joint, optimal_1$pred)^2 %>%
  round(2)
R2_descriptive_1 <- cor(descriptive_1$joint, descriptive_1$pred)^2 %>%
  round(2)
R2_auditory_1  <- cor(auditory_1$joint, auditory_1$pred)^2 %>%
  round(2)
R2_visual_1  <- cor(visual_1$joint, visual_1$pred)^2 %>%
  round(2)

#Exp 2
optimal_2 <- subset(models_all, model=='Optimal' & experiment=='Experiment 2')
descriptive_2 <- subset(models_all, model=='Descriptive' & experiment=='Experiment 2')
auditory_2 <- subset(models_all, model=='Auditory' & experiment=='Experiment 2')
visual_2 <- subset(models_all, model=='Visual' & experiment=='Experiment 2')

R2_optimal_2  <- cor(optimal_2$joint, optimal_2$pred)^2  %>%
  round(2)
R2_descriptive_2 <- cor(descriptive_2$joint, descriptive_2$pred)^2 %>%
  round(2)
R2_auditory_2  <- cor(auditory_2$joint, auditory_2$pred)^2 %>%
  round(2)
R2_visual_2  <- cor(visual_2$joint, visual_2$pred)^2 %>%
  round(2)

#Exp 3
optimal_3 <- subset(models_all, model=='Optimal' & experiment=='Experiment 3')
descriptive_3 <- subset(models_all, model=='Descriptive' & experiment=='Experiment 3')
auditory_3 <- subset(models_all, model=='Auditory' & experiment=='Experiment 3')
visual_3 <- subset(models_all, model=='Visual' & experiment=='Experiment 3')

R2_optimal_3  <- cor(optimal_3$joint, optimal_3$pred)^2 %>%
  round(2)
R2_descriptive_3 <- cor(descriptive_3$joint, descriptive_3$pred)^2 %>%
  round(2)
R2_auditory_3  <- cor(auditory_3$joint, auditory_3$pred)^2 %>%
  round(2)
R2_visual_3  <- cor(visual_3$joint, visual_3$pred)^2 %>%
  round(2)

@@

correlation_plot

@@

##Here we fit logistic regression to each participant
##The logitic regression is equivalent to the descriptive model without the bias term
##We use logistic regressions  instead of the full descriptive model becuase the latter would not converge given the small data points available for each participant

joint_bysub_1 <- joint_all_exp1 %>%
  group_by(ID) %>%
  do(fit_joint_1 = glm(answer ~ concept_dist+ sound_dist, data=., family = binomial()))

joint_bysub_2 <- joint_all_exp2 %>%
  group_by(ID) %>%
  do(fit_joint_2 = glm(answer ~ concept_dist+ sound_dist, data=., family = binomial()))

joint_bysub_3 <- joint_all_exp3 %>%
  group_by(ID) %>%
  do(fit_joint_3 = glm(answer ~ concept_dist+ sound_dist, data=., family = binomial()))

##Extract auitory and visual variances for each participant

>>>>

```{r load_packages, include = FALSE}
library(papaja)
library(readr)
library(tidyr)
library(ggplot2)
library(cowplot)
library(knitr)
library(boot)
library(dplyr)
library(langcog)
library(ggthemes)
library(broom)
library(kableExtra)
#library("knitcitations")
#cleanbib()
#options("citation_format" = "pandoc")
```

@@

exp4 <- read_delim("../Data_and_analysis/data_rev_real1.txt", delim = " ") %>%
  filter(type == "Task") %>%
  mutate(experiment='Experiment1')

@@

N_all_4 <- exp4 %>%
  distinct(ID) %>%
  nrow()

@@

#Exp 4
exp4_noProb <- exp4 %>%
  filter(problem=="No")

N_noProb_4 <- exp4_noProb %>%
  distinct(ID) %>%
  nrow()

@@

#Exp 4 (The change in the selection threshold in 1 bis was re-registered: the longer experiment required stricter quality control)
exp4_good <- exp4_noProb %>%
  filter(score >= 0.75)

N_good_4 <- exp4_good %>%
  distinct(ID) %>%
  nrow()
```

@@

```{r model, out.width = '\\textwidth', fig.pos = "!h", fig.cap = "Illustration of the model using simulated data. A word category is defined as the joint bivariate distribution of an auditory category (horizontal, bottom panel) and a visual semantic category (vertical, left panel). Upon the presentation of a word token $w$, participants guess whether it is sampled from the word type $W_1$ or from the word type $W_2$. Decision threshold is where the guessing probability is 0.5."}
knitr::include_graphics("pictures/model.png", dpi = 108)
```

@@

@@

Although the paradigm is within-subjects, we did not have enough statistical power to fit a different model for each individual participant. Instead, models were constructed with data collapsed across all participants. The fit was done with a nonlinear least squares regression using the NLS package in R [@bates88]. We computed the values of the parameters, as well as their 95% confidence intervals, through non-parametric bootstrap (using 10000 iterations).

```{r stats, results="asis", echo=FALSE}

parameters <- feather::read_feather("../Data_and_analysis/saved_data/parameters.feather")

kable(parameters, format = "latex", escape = FALSE, booktabs = TRUE,
      linesep = "", format.args = list(big.mark = ","),
      caption = "Statistics for the dataset we used."#,
      #col.names = c("Language",  "Nouns", "Ages", "N", "Nouns", "Ages","N")
      ) %>%
  add_header_above(c("", "Auditory" = 2, "Visual" = 2, "Bimodal" = 3 )) %>%
  column_spec(1, bold = TRUE) %>%
  kable_styling(position = "center")

@@

exp_uni <- feather::read_feather("../Data_and_analysis/saved_data/exp_uni.feather")
pred_uni <- feather::read_feather("../Data_and_analysis/saved_data/pred_uni.feather")

### plot unimodal data + fit functions 
ggplot(exp_uni, 
       aes(x = distance, y = mean)) + 
  #geom_point()+
  geom_pointrange(aes(ymin = lower, ymax = upper), 
                  position = position_dodge(width = .1), size = 0.4, fatten = 2) + 
  #geom_line(data=uniV,aes(x=xV, y=yV))+
  geom_line(data=pred_uni, aes(x=distance, y=prediction), col='black')+
  xlab("Distance") +ylab("Prob. different")+
  scale_y_continuous(limits = c(0, 1))+#theme(aspect.ratio = 0.7)+
  theme_few()+
  theme(aspect.ratio = 0.7) + facet_grid(experiment ~ Condition)
  #stat_function(fun = Logistic_v, colour="red"))

@@

@@

pred_bimod <- feather::read_feather("../Data_and_analysis/saved_data/all_bimod.feather")

pred_bimod$model <- factor(pred_bimod$model, levels = c('Visual','Auditory', 'Optimal', 'Descriptive'))

ggplot(pred_bimod, 
       aes(x = pred, y = Joint, col = factor(concept_dist), 
           shape = factor(sound_dist))) + 
  geom_point(size =1)+
  scale_colour_solarized()+
 #geom_pointrange(aes(ymin = summary_ci_lower, ymax = summary_ci_upper), 
  #                position = position_dodge(width = .1), size=0.2) +

  geom_abline(slope = 1, lty = 2) +
  #annotate("text",aes(label=paste("R^2 ==", cor, sep="")), x=0.1, y=0.9, size=2, col='black', fontface = "bold", parse=TRUE)+
  geom_text(aes(label=paste("r^2 ==", cor, sep="")), x=0.15, y=0.9, size=2, col='black',fontface = "bold", parse=TRUE)+
  xlab("Predictions") +ylab("Human data")+
  facet_grid(experiment ~ model)+
  theme_few()+
theme(aspect.ratio = 0.7, 
      axis.text=element_text(size=6),
      strip.text.y = element_text(size = 8))+
  guides(color=guide_legend(title="Visual Distance")) +
  guides(shape=guide_legend(title="Auditory Distance"))

@@

<!--the model addresses the question of optimality at the population level. However, it is important to  know how individual responses are distributed. In fact, one could think of an extreme case where optimality at the population level would be misleading. Imagine, for instance, that in the bimodal condition half the participants relied exclusively on the visual modality, whereas the other half relied exclusively on the auditory modality. This case could still lead to an aggregate behavior which appears optimal, but this optimality would be spurious.

As a second analysis, we asked whether the observed variance in the individual distribution was due to mere sampling errors or whether it corresponded to a real between-subject variability. We simulated individual responses from the posterior distribution whose parameters were fit to the population as a whole (i.e., the descriptive posterior). The resulting distribution is shown in Figure\ \@ref(fig:individual). For ease of comparison, the simulated distribution was superimposed to the real distribution. We found that the real distribution had a standard deviation of $sd=$ `r subset(sd_ind, data=='real')$sd` which was larger than that of the simulated distribution ($sd=$ `r subset(sd_ind, data=='simulation')$sd`), indicating that there was real between-subject variation beyond sampling errors. This finding means that the participants varied in terms of how they weighted modalities: Compared to the predictions of the population-level model, some participants relied more on the auditory modality, whereas others relied more on the visual modality. -->
